Selection on early survival does not explain germination rate clines in *Mimulus cardinalis* (Phrymaceae)

### 2021-12-14 ms/ms.Rmd
rearranged target order

---
title: 'Selection on early survival does not explain germination rate clines in *Mimulus cardinalis* (Phrymaceae)'
author: "Christopher D. Muir$^{1,2,*}$, Courtney L. Van Den Elzen$^{1,3}$, Amy L. Angert$^{1,4}$"
output:
  bookdown::pdf_document2:
    includes:
      before_body: ../template/doc_prefix.tex
      in_header: ../template/preamble.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc: no
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::word_document2: null
fontsize: 12pt
linestretch: 1.5
link-citations: yes
csl: ../template/american-journal-of-botany.csl
bibliography: ../ms/mimulus-germination.bib
---

@@

Manuscript received _______; revision accepted _______.

*short title*: Selection on germination in *Mimulus cardinalis*

>>>>

---
title: 'Selection on early survival does not explain germination rate clines in *Mimulus cardinalis* (Phrymaceae)'
author: "Christopher D. Muir$^{1,2,*}$, Courtney L. Van Den Elzen$^{1,3}$, Amy L. Angert$^{1,4}$"
output:
  bookdown::pdf_document2:
    includes:
      before_body: ../template/doc_prefix.tex
      in_header: ../template/preamble.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc: no
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::word_document2: null
fontsize: 12pt
linestretch: 1
link-citations: yes
csl: ../template/american-journal-of-botany.csl
bibliography: ../ms/mimulus-germination.bib
---

@@

<!-- Manuscript received _______; revision accepted _______. -->

<!-- *short title*: Selection on germination in *Mimulus cardinalis* -->
